---
title: "stanflow (Stan Bayesian Workflow)"
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
    fig.path: "man/figures/README-"
    out.width: "100%"
format: gfm
cache: true
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/VisruthSK/stanflow/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/VisruthSK/stanflow/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/VisruthSK/stanflow/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/VisruthSK/stanflow/actions/workflows/pkgdown.yaml)
[![check-interfaces](https://github.com/VisruthSK/stanflow/actions/workflows/interfaces.yaml/badge.svg)](https://github.com/VisruthSK/stanflow/actions/workflows/interfaces.yaml)
<!-- badges: end -->

NB: `stanflow` is currently under active development--breaking changes may be made without warning, until a proper release (see the v1.0.0 milestone).

---

`stanflow` is a R package for a mildly opinionated Stan based [Bayesian Workflow](https://arxiv.org/abs/2011.01808) (Gelman et al. 2020). Much like the famous [tidyverse package](https://github.com/tidyverse/tidyverse), `stanflow` is a metapackage which installs and attaches relevant Stan R packages, serving as a one-stop-shop for Bayesian modelling. `stanflow` draws heavy inspiration from `tidyverse`, and reuses portions of its codebase--however, `stanflow` eschews `tidyverse` packages (i.e., `purrr`, `dplyr`, etc.) for base R.

## Features

* Install common Stan packages in one step[^1]:
  * Installing/loading `stanflow` loads `bayesplot`, `loo`, `posterior`, `projpred`, and `shinystan`
* Generate proper Stan citations for your research project:
  * `stan_cite()` scans a directory (or a provided list of files) to find all used Stan functions, and outputs a BibTeX with the correct citations for every package and function you used.
* Setup Stan interfaces:
  * `setup_interface()` automatically handles installing/updating/loading any of the compatible Stan backends: `brms`, `cmdstanr`, `rstan`, `rstanarm`, with some mild defaults.
* Update packages[^1]:
  * `stanflow_update()` attempts to automatically update out of date packages, and can optionally search for dependencies' dependencies. `stanflow` natively relies on the [`multiverse`](https://r-multiverse.org/) for stable releases (see `stan_repos`).

[^1]: This feature is adopted from the `tidyverse` package!

There are a few more functions, but these four are the heart of `stanflow` and what you will probably use the most.

## Installation

You can install the development version of stanflow from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("VisruthSK/stanflow")
```

## Usage

Here, we load `stanflow` and use `cmdstanr` as the backend for `brms`.

```{r}
library(stanflow)
setup_interface(
  interface = "brms",
  brms_backend = "cmdstanr",
  cores = 2
)
set.seed(0)
flow_check()
```

With the first two commands, users have access to everything they need to fit and interrogate Bayesian models. Specifically, those two commands will load the core stanflow packages: `bayesplot`, `loo`, `posterior`, `projpred` and `shinystan`, as well as setup `brms` to use the `cmdstanr` backend with 2 cores. These packages (including `brms` and `cmdstanr`) are all "`library()`d" as well, so we can proceed with our analysis immediately.

```{r}
cmdstanr_example()

fit1 <- brm(
  count ~ zAge + zBase * Trt + (1 | patient),
  data = epilepsy,
  family = poisson(),
  silent = TRUE,
  refresh = 0
)
summary(fit1)

plot(fit1, variable = c("b_Trt1", "b_zBase"))

fit2 <- brm(
  count ~ zAge + zBase * Trt + (1 | patient) + (1 | obs),
  data = epilepsy,
  family = poisson(),
  silent = TRUE,
  refresh = 0
)
summary(fit2)

loo(fit1, fit2)
```

Code snippets above are taken from the [`brms` README](https://paulbuerkner.com/brms/) but results aren't directly comparable.
